On penalty flux parameters in first order DG formulations

### 2016-10-20 docs/dg_penalty/main.tex
updating note

\usetikzlibrary{calc}

%%% START MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.
\newcommand{\logLogSlopeTriangle}[5]
{
    % #1. Relative offset in x direction.
    % #2. Width in x direction, so xA-xB.
    % #3. Relative offset in y direction.
    % #4. Slope d(y)/d(log10(x)).
    % #5. Plot options.

    \pgfplotsextra
    {
        \pgfkeysgetvalue{/pgfplots/xmin}{\xmin}
        \pgfkeysgetvalue{/pgfplots/xmax}{\xmax}
        \pgfkeysgetvalue{/pgfplots/ymin}{\ymin}
        \pgfkeysgetvalue{/pgfplots/ymax}{\ymax}

        % Calculate auxilliary quantities, in relative sense.
        \pgfmathsetmacro{\xArel}{#1}
        \pgfmathsetmacro{\yArel}{#3}
        \pgfmathsetmacro{\xBrel}{#1-#2}
        \pgfmathsetmacro{\yBrel}{\yArel}
        \pgfmathsetmacro{\xCrel}{\xArel}

        \pgfmathsetmacro{\lnxB}{\xmin*(1-(#1-#2))+\xmax*(#1-#2)} % in [xmin,xmax].
        \pgfmathsetmacro{\lnxA}{\xmin*(1-#1)+\xmax*#1} % in [xmin,xmax].
        \pgfmathsetmacro{\lnyA}{\ymin*(1-#3)+\ymax*#3} % in [ymin,ymax].
        \pgfmathsetmacro{\lnyC}{\lnyA+#4*(\lnxA-\lnxB)}
        \pgfmathsetmacro{\yCrel}{\lnyC-\ymin)/(\ymax-\ymin)} % THE IMPROVED EXPRESSION WITHOUT 'DIMENSION TOO LARGE' ERROR.

        % Define coordinates for \draw. MIND THE 'rel axis cs' as opposed to the 'axis cs'.
        \coordinate (A) at (rel axis cs:\xArel,\yArel);
        \coordinate (B) at (rel axis cs:\xBrel,\yBrel);
        \coordinate (C) at (rel axis cs:\xCrel,\yCrel);

        % Draw slope triangle.
        \draw[#5]   (A)-- node[pos=0.5,anchor=north] {1}
                    (B)-- 
                    (C)-- node[pos=0.5,anchor=west] {#4}
                    cycle;
    }
}
%%% END MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.

\newcommand{\logLogSlopeTriangleNeg}[5]
{
    % #1. Relative offset in x direction.
    % #2. Width in x direction, so xA-xB.
    % #3. Relative offset in y direction.
    % #4. Slope d(y)/d(log10(x)).
    % #5. Plot options.

    \pgfplotsextra
    {
        \pgfkeysgetvalue{/pgfplots/xmin}{\xmin}
        \pgfkeysgetvalue{/pgfplots/xmax}{\xmax}
        \pgfkeysgetvalue{/pgfplots/ymin}{\ymin}
        \pgfkeysgetvalue{/pgfplots/ymax}{\ymax}

        % Calculate auxilliary quantities, in relative sense.
        \pgfmathsetmacro{\xArel}{#1}
        \pgfmathsetmacro{\yArel}{#3}
        \pgfmathsetmacro{\xBrel}{#1-#2}
        \pgfmathsetmacro{\yBrel}{\yArel}
        \pgfmathsetmacro{\xCrel}{\xArel}

        \pgfmathsetmacro{\lnxB}{\xmin*(1-(#1-#2))+\xmax*(#1-#2)} % in [xmin,xmax].
        \pgfmathsetmacro{\lnxA}{\xmin*(1-#1)+\xmax*#1} % in [xmin,xmax].
        \pgfmathsetmacro{\lnyA}{\ymin*(1-#3)+\ymax*#3} % in [ymin,ymax].
        \pgfmathsetmacro{\lnyC}{\lnyA+#4*(\lnxA-\lnxB)}
        \pgfmathsetmacro{\yCrel}{\lnyC-\ymin)/(\ymax-\ymin)} % THE IMPROVED EXPRESSION WITHOUT 'DIMENSION TOO LARGE' ERROR.

        % Define coordinates for \draw. MIND THE 'rel axis cs' as opposed to the 'axis cs'.
        \coordinate (A) at (rel axis cs:\xArel,\yArel);
        \coordinate (B) at (rel axis cs:\xBrel,\yBrel);
        \coordinate (C) at (rel axis cs:\xCrel,\yCrel);

        % Draw slope triangle.
        \draw[#5]   (A)-- node[pos=.5,anchor=south] {1}
                    (B)-- 
                    (C)-- node[pos=0.5,anchor=west] {#4}
                    cycle;
    }
}
%%% END MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.

%%% START MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.
\newcommand{\logLogSlopeTriangleFlipNeg}[5]
{
    % #1. Relative offset in x direction.
    % #2. Width in x direction, so xA-xB.
    % #3. Relative offset in y direction.
    % #4. Slope d(y)/d(log10(x)).
    % #5. Plot options.

    \pgfplotsextra
    {
        \pgfkeysgetvalue{/pgfplots/xmin}{\xmin}
        \pgfkeysgetvalue{/pgfplots/xmax}{\xmax}
        \pgfkeysgetvalue{/pgfplots/ymin}{\ymin}
        \pgfkeysgetvalue{/pgfplots/ymax}{\ymax}

        % Calculate auxilliary quantities, in relative sense.
        %\pgfmathsetmacro{\xArel}{#1}
        %\pgfmathsetmacro{\yArel}{#3}
        \pgfmathsetmacro{\xBrel}{#1-#2}
        \pgfmathsetmacro{\yBrel}{#3}
        \pgfmathsetmacro{\xCrel}{#1}

        \pgfmathsetmacro{\lnxB}{\xmin*(1-(#1-#2))+\xmax*(#1-#2)} % in [xmin,xmax].
        \pgfmathsetmacro{\lnxA}{\xmin*(1-#1)+\xmax*#1} % in [xmin,xmax].
        \pgfmathsetmacro{\lnyA}{\ymin*(1-#3)+\ymax*#3} % in [ymin,ymax].
        \pgfmathsetmacro{\lnyC}{\lnyA+#4*(\lnxA-\lnxB)}
        \pgfmathsetmacro{\yCrel}{\lnyC-\ymin)/(\ymax-\ymin)} % THE IMPROVED EXPRESSION WITHOUT 'DIMENSION TOO LARGE' ERROR.

	\pgfmathsetmacro{\xArel}{\xBrel}
        \pgfmathsetmacro{\yArel}{\yCrel}

        % Define coordinates for \draw. MIND THE 'rel axis cs' as opposed to the 'axis cs'.
        \coordinate (A) at (rel axis cs:\xArel,\yArel);
        \coordinate (B) at (rel axis cs:\xBrel,\yBrel);
        \coordinate (C) at (rel axis cs:\xCrel,\yCrel);

        % Draw slope triangle.
        \draw[#5]   (A)-- node[pos=0.5,anchor=east] {#4}
                    (B)-- 
                    (C)-- node[pos=0.5,anchor=north] {1}
                    cycle;
    }
}
%%% END MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.

%%% START MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.
\newcommand{\logLogSlopeTriangleFlip}[5]
{
    % #1. Relative offset in x direction.
    % #2. Width in x direction, so xA-xB.
    % #3. Relative offset in y direction.
    % #4. Slope d(y)/d(log10(x)).
    % #5. Plot options.

    \pgfplotsextra
    {
        \pgfkeysgetvalue{/pgfplots/xmin}{\xmin}
        \pgfkeysgetvalue{/pgfplots/xmax}{\xmax}
        \pgfkeysgetvalue{/pgfplots/ymin}{\ymin}
        \pgfkeysgetvalue{/pgfplots/ymax}{\ymax}

        % Calculate auxilliary quantities, in relative sense.
        %\pgfmathsetmacro{\xArel}{#1}
        %\pgfmathsetmacro{\yArel}{#3}
        \pgfmathsetmacro{\xBrel}{#1-#2}
        \pgfmathsetmacro{\yBrel}{#3}
        \pgfmathsetmacro{\xCrel}{#1}

        \pgfmathsetmacro{\lnxB}{\xmin*(1-(#1-#2))+\xmax*(#1-#2)} % in [xmin,xmax].
        \pgfmathsetmacro{\lnxA}{\xmin*(1-#1)+\xmax*#1} % in [xmin,xmax].
        \pgfmathsetmacro{\lnyA}{\ymin*(1-#3)+\ymax*#3} % in [ymin,ymax].
        \pgfmathsetmacro{\lnyC}{\lnyA+#4*(\lnxA-\lnxB)}
        \pgfmathsetmacro{\yCrel}{\lnyC-\ymin)/(\ymax-\ymin)} % THE IMPROVED EXPRESSION WITHOUT 'DIMENSION TOO LARGE' ERROR.

	\pgfmathsetmacro{\xArel}{\xBrel}
        \pgfmathsetmacro{\yArel}{\yCrel}

        % Define coordinates for \draw. MIND THE 'rel axis cs' as opposed to the 'axis cs'.
        \coordinate (A) at (rel axis cs:\xArel,\yArel);
        \coordinate (B) at (rel axis cs:\xBrel,\yBrel);
        \coordinate (C) at (rel axis cs:\xCrel,\yCrel);

        % Draw slope triangle.
        \draw[#5]   (A)-- node[pos=0.5,anchor=east] {#4}
                    (B)-- 
                    (C)-- node[pos=0.5,anchor=south] {1}
                    cycle;
    }
}
%%% END MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.

%% ====================================== macros

@@

\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\avg}[1] {\ensuremath{\LRc{\!\{#1\}\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\Bh}{\widehat{B}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\Lk}{L^2\LRp{D^k}}
\newcommand{\Dhat}{\widehat{D}}
\newcommand{\Lhat}{L^2\LRp{\Dhat}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

@@

\date{}
\author{Jesse Chan}
\title{On the penalty parameter in first order DG formulations}

@@

We consider a first order system of hyperbolic equations
\[
\bm{A}_0\pd{\bm{U}}{t} + \sum_{i=1}^d \pd{\bm{F}_i(\bm{U})}{\bm{x}_i} = 0,
\]
which may alternatively be written as
\[
\bm{A}_0\pd{\bm{U}}{t} + \sum_{i=1}^d \pd{\LRp{\bm{A}_{i}U}}{\bm{x}_i}, \qquad \bm{A}_{i} = \pd{\bm{F}_i(\bm{U})}{\bm{U}}
\]
where $\bm{A}_{i}$ are symmetric matrices.  The semi-discrete DG formulation for such systems may be written as 
\[
\sum_{D^k \in \Oh} \LRp{\bm{A}_0\pd{\bm{U}}{t},\bm{V} }_{\Lk} = \sum_{D^k \in \Oh}\LRp{ \LRp{\bm{F}_i(\bm{U}), \bm{V}_{,i}}_{\Lk} - \LRa{\bm{F}_i^*(\bm{U})\bm{n}_i,\bm{V}}_{\partial D^k}}
\]
where $\bm{n}$ is the outward normal on a face $f$ of $D^k$, and $\bm{F^*}$ is a numerical flux depending defined on shared faces between two elements.

For convergence, $\bm{F^*} = \bm{F^*}(\bm{U})$ must be consistent such that, for exact solutions $\bm{U}$, 
\[
\bm{F^*} = \bm{F}(\bm{U}).
\]
Let $f$ be a shared face between two elements $D^{k,+}$ and $D^{k,-}$, and let $\bm{F}^+, \bm{F}^-$ be evaluations of $\bm{F}(\bm{U})$ restricted to $D^{k,+}$ and $D^{k,-}$, respectively.  Typical DG fluxes are defined as the sum of a consistent averaging of $\bm{F}^+$ and $\bm{F}^-$ and a penalization term
\begin{equation}
\bm{F^*} = \avg{\bm{F}_n(\bm{U})} - \bm{W}\jump{\bm{U}},
\label{eq:flux}
\end{equation}
where $\bm{W}$ is some positive-definite matrix, which is required for energy stability.

The upwind numerical flux is a well-known flux of the form (\ref{eq:flux}).  For some normal vector $\bm{n}$, let $\jump{\bm{A}_n} = \sum_{i=1}^d \jump{\bm{A}_i\bm{n}_i}$.  By \note{add citation}, $\jump{\bm{A}_n}$ contains real eigenvalues, and admits an eigenvalue decomposition
\[
\jump{\bm{A}_n} = \bm{V}{\bm{\Lambda}}\bm{V}^{-1}, \qquad \bm{\Lambda} = 
\left(\begin{array}{ccc}
\lambda_1 & & \\
& \ddots & \\
& & \lambda_d
\end{array}\right).
\]
For problems with continuous coefficients, the upwind numerical flux can be defined as
\[
\bm{F^*} = \bm{A}^+\bm{U}^- + \bm{A}^- \bm{U}^+,
\]
where the matrices $\bm{A}^+,\bm{A}^-$ are constructed from the positive and negative eigenvalues 
\begin{align*}
\bm{A}^+ &= \frac{1}{2}\bm{V} \LRp{\bm{\Lambda} + \LRb{\bm{\Lambda}}} \bm{V}^{-1}\\
\bm{A}^- &= \frac{1}{2}\bm{V} \LRp{\bm{\Lambda} - \LRb{\bm{\Lambda}}} \bm{V}^{-1},
\end{align*}
and $\LRb{\Lambda}$ is the diagonal matrix whose entries consist of the absolute values of the eigenvalues $\LRb{\lambda_i}$.  This can be rewritten as
\[
\bm{F^*} = \avg{\bm{A}\bm{U}} - \bm{V}\LRb{\bm{\Lambda}}\bm{V}^{-1} \jump{\bm{U}}.  
\]

An alternative to upwind fluxes are penalty fluxes, which penalize appropriately defined jumps of the solution.  One such penalty flux is given as
\[
\bm{F^*} = \avg{\bm{A}\bm{U}} - \bm{A}^T \bm{W} \jump{\bm{A}\bm{U}}.  
\]
where $\bm{W}$ is some positive-definite weighting matrix.  In contrast to Lax-Friedrichs fluxes, the penalty flux enforce a weaker continuity.

\subsection{Example: acoustic wave equation}

Consider the isotropic acoustic wave equation in pressure-velocity form
\begin{align*}
\pd{p}{t} &= \Div \bm{u}\\
\pd{\bm{u}}{t} &= \Grad p.
\end{align*}
Let $\bm{U}$ denote the group variable $\bm{U} = (p,u,v)$, where $u$ and $v$ are the $x$ and $y$ components of velocity.  Then, in two dimensions, the isotropic wave equation is given as
\[
\pd{\bm{U}}{t} + \pd{\bm{A}_x\bm{U}}{x} + \pd{\bm{A}_y\bm{U}}{y} = 0, \qquad \bm{A}_x = 
\left(\begin{array}{ccc}
0 & 1 & 0\\
1 & 0 & 0\\
0 & 0 & 0
\end{array}
\right), \qquad 
\bm{A}_y = 
\left(\begin{array}{ccc}
0 & 0 & 1\\
0 & 0 & 0\\
1 & 0 & 0
\end{array}
\right).
\]
The normal flux matrix $\bm{A}_n$ is then
\[
\bm{A}_n = 
\left(\begin{array}{ccc}
0 & \bm{n}_x & \bm{n}_y\\
\bm{n}_x & 0 & 0\\
\bm{n}_y & 0 & 0
\end{array}
\right)
\]
implying that the penalty fluxes (with $\bm{W} = \tau\bm{I}$) are 
\[
\avg{\bm{A}_n \bm{U}} - \bm{A}_n^T \jump{\bm{A}_n\bm{U}} = \left(\begin{array}{c}
\avg{\bm{u}_n}\\
\avg{p }\bm{n}_x\\
\avg{p }\bm{n}_y
\end{array}
\right) - 
\tau\left(\begin{array}{c}
\jump{p}\\
\jump{\bm{u_n}}\bm{n}_x\\
\jump{\bm{u_n}}\bm{n}_y
\end{array}
\right)
\]
For $\tau = 1$, these fluxes coincide with the upwind fluxes.

@@

\note{Reproduce Gershgorin proof here.}
We split the DG approximation space into conforming and non-conforming parts, which induces a block matrix
\[
\bm{K} = \left(\begin{array}{cc}
\bm{A} & \bm{B}\\
-\bm{B}^T & \bm{C} + \tau \bm{S}
\end{array}\right).
\]
We will adapt the proof presented in \cite{Warburton20063205} to show that the spectra of $\bm{K}$ splits into two sets as $\tau\rightarrow \infty$, the first of which approaches the eigenvalues of $\bm{A}$, and the second of which moves left of the imaginary axis at a rate of $O(\tau)$.

We first consider the spectra of $\bm{C} + \tau\bm{S}$.  By the construction of the DG formulation $\bm{C}$ is skew-symmetric, while $\bm{S}$ is symmetric and negative-definite.  Let $\lambda, \bm{u}$ be an eigenpair of $\bm{C} + \tau{\bm{S}}$ corresponding to the largest $N^D$ eigenvalues. Let $\lambda = \alpha + i\beta$ and $\bm{u} = \bm{v} + i\bm{w}$, where $\alpha,\beta$ and $\bm{v},\bm{w}$ are the real and imaginary parts of $\lambda$ and $\bm{u}$, respectively.  Then, expanding and grouping terms in
\[
(\bm{C}+\tau\bm{S})(\bm{v} + i\bm{w}) = (\alpha + i\beta) (\bm{v} + i\bm{w})
\]
we have that
\begin{align*}
(\bm{C}+\tau\bm{S})\bm{v} &= \alpha\bm{v}-\beta\bm{w}\\
(\bm{C}+\tau\bm{S})\bm{w} &= \beta\bm{v}+\alpha\bm{w}.
\end{align*}
Assuming that $\bm{u}^*\bm{u} = \nor{\bm{v}}^2 + \nor{\bm{w}}^2 = 1$, multiplying both sides by $\bm{v}^T,\bm{w}^T$ and straightforward manipulations %yield
%\begin{align*}
%\bm{v}^T\bm{A}\bm{v} &= \alpha\nor{\bm{v}}^2-\beta\bm{v}^T\bm{w}\\
%\bm{w}^T\bm{A}\bm{w} &= \beta\bm{w}^T{\bm{v}}+\alpha\nor{\bm{w}}^2.  
%\end{align*}
%\begin{align*}
%\bm{v}^T\bm{A}\bm{v} + \bm{w}^T\bm{A}\bm{w} &= \alpha\\
%\bm{v}^T\bm{A}\bm{w} - \bm{w}^T\bm{A}\bm{w} &= \beta.
%\end{align*}
using the skew-symmetry of $\bm{C}$ and symmetry of $\bm{S}$ yields
\begin{align*}
\bm{v}^T\bm{C}\bm{w} - \bm{w}^T\bm{C}\bm{w} &= \beta\\
\tau\LRp{\bm{v}^T\bm{S}\bm{v} + \bm{w}^T\bm{S}\bm{w}} &= \alpha.
\end{align*}
Since $\bm{v}^T\bm{C}\bm{w} - \bm{w}^T\bm{C}\bm{w}= 2\bm{w}^T\bm{C}\bm{v} = \beta$ is independent of $\tau$ and $\bm{v},\bm{w}$ are normalized, $\beta$ remains bounded as $\tau\rightarrow \infty$.  Similarly, since $\bm{S}$ is symmetric, negative-definite, and independent of $\tau$, the quantity
\[
\LRb{\bm{v}^T\bm{S}\bm{v} + \bm{w}^T\bm{S}\bm{w}} = \LRb{\frac{\alpha}{\tau}}
\]
is bounded independently of $\tau$, and we conclude that $\LRb{\alpha} = O(\tau)$.  Thus, as $\tau$ increases, the eigenvalues of $\bm{C} + \tau\bm{S}$ are shifted further and further left of the imaginary axis.

\subsection{Bifurcation of eigenvalue sets}

>>>>

\usetikzlibrary{calc}
\usepackage{stmaryrd}

@@

\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\llbracket#1\rrbracket}}
\newcommand{\avg}[1] {\ensuremath{\LRc{\!\{#1\}\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\Bh}{\widehat{B}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\Lk}{L^2\LRp{D^k}}
\newcommand{\Dhat}{\widehat{D}}
\newcommand{\Lhat}{L^2\LRp{\Dhat}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

@@

\date{}
\author{Jesse Chan, T. Warburton}
\title{On penalty flux parameters in first order DG formulations}

@@

We consider a first order system of hyperbolic equations
\[
\bm{A}_0\pd{\bm{U}}{t} + \sum_{i=1}^d \pd{\bm{F}_i(\bm{U})}{\bm{x}_i} = 0,
\]
which may alternatively be written as
\[
\bm{A}_0\pd{\bm{U}}{t} + \sum_{i=1}^d \pd{\LRp{\bm{A}_{i}U}}{\bm{x}_i}, \qquad \bm{A}_{i} = \pd{\bm{F}_i(\bm{U})}{\bm{U}}
\]
where $\bm{A}_{i}$ are symmetric matrices.  The semi-discrete DG formulation for such systems may be written as 
\[
\sum_{D^k \in \Oh} \LRp{\bm{A}_0\pd{\bm{U}}{t},\bm{V} }_{\Lk} = \sum_{D^k \in \Oh}\LRp{ \LRp{\bm{F}_i(\bm{U}), \bm{V}_{,i}}_{\Lk} - \LRa{\bm{F}_n^*(\bm{U})\bm{n}_i,\bm{V}}_{\partial D^k}}
\]
where $\bm{n}$ is the outward normal on a face $f$ of $D^k$, and $\bm{F^*}_n$ is a numerical flux depending defined on shared faces between two elements.

%For convergence, $\bm{F^*}_n = \bm{F^*}_n(\bm{U})$ must be consistent such that, for exact solutions $\bm{U}$, 
%\[
%\bm{F^*}_n = \bm{F}(\bm{U})\cdot \bm{n}.
%\]

Let $f$ be a shared face between two elements $D^{k,+}$ and $D^{k,-}$, and let $\bm{F}^+, \bm{F}^-$ be evaluations of $\bm{F}(\bm{U})$ restricted to $D^{k,+}$ and $D^{k,-}$, respectively.  The average and jump of a vector valued function over $f$ are then defined as
\[
\avg{\bm{F}} = \frac{\bm{F}^+ + \bm{F}^-}{2}, \qquad \jump{\bm{F}} = \bm{F}^+ - \bm{F}^-.
\]
Typical numerical fluxes are defined as the sum of the average of $\bm{F}^+$ and $\bm{F}^-$ and a penalization term
\begin{equation}
\bm{F^*}_n = \avg{\bm{F}(\bm{U})}\cdot \bm{n} - \bm{G}\LRp{\jump{\bm{U}}},
\label{eq:flux}
\end{equation}
where $\bm{G}$ is some convex function.

The upwind numerical flux is a well-known flux of the form (\ref{eq:flux}).  For some normal vector $\bm{n}$, let ${\bm{A}}_n = \sum_{i=1}^d {\bm{A}_i\bm{n}_i}$.  By \note{add citation}, ${\bm{A}}_n$ contains real eigenvalues, and admits an eigenvalue decomposition
\[
\bm{A}_n = \bm{V}{\bm{\Lambda}}\bm{V}^{-1}, \qquad \bm{\Lambda} = 
\left(\begin{array}{ccc}
\lambda_1 & & \\
& \ddots & \\
& & \lambda_d
\end{array}\right).
\]
For problems with continuous coefficients, the upwind numerical flux can be defined as
\[
\bm{F^*}_n = \bm{A}_n^+\bm{U}^- + \bm{A_n}^- \bm{U}^+,
\]
where the matrices $\bm{A_n}^+,\bm{A_n}^-$ are constructed from the positive and negative eigenvalues 
\begin{align*}
\bm{A}_n^+ &= \frac{1}{2}\bm{V} \LRp{\bm{\Lambda} + \LRb{\bm{\Lambda}}} \bm{V}^{-1}\\
\bm{A}_n^- &= \frac{1}{2}\bm{V} \LRp{\bm{\Lambda} - \LRb{\bm{\Lambda}}} \bm{V}^{-1},
\end{align*}
and $\LRb{\bm{\Lambda}}$ is the diagonal matrix whose entries consist of the absolute values of the eigenvalues $\LRb{\lambda_i}$.  This can be rewritten as the sum of the central flux and a penalization
\[
\bm{F^*}_n = \avg{\bm{A}_n\bm{U}} - \tau\bm{V}\LRb{\bm{\Lambda}}\bm{V}^{-1} \jump{\bm{U}}.  
\]
For problems with discontinuous coefficients, this may be generalized by solving a Riemann problem to yield
\[
\bm{F^*}_n = \avg{\bm{A}_n\bm{U}} - \tau \jump{{\bm{V}\LRb{\bm{\Lambda}}\bm{V}^{-1}\bm{U}}}.  
\]

An alternative to upwind fluxes are penalty fluxes, which penalize appropriately defined jumps of the solution.  One such penalty flux is 
\[
\bm{F^*}_n = \avg{\bm{A}_n\bm{U}} - \bm{A}_n^T \bm{W} \jump{\bm{A}_n\bm{U}}.  
\]
where $\bm{W}$ is a diagonal weighting matrix with positive entries.  We take $\bm{W} = \tau \bm{I}$ in the following sections; however, the entries can be made to vary.  For example, taking $\bm{W} = \LRb{\bm{\Lambda}}^{-1}$ recovers the upwind fluxes \note{prove this}.
%\[
%\bm{F^*}_n = \avg{\bm{A}_n\bm{U}} - \bm{A}_n^T \LRb{\bm{Lambda}}^{-1} \jump{\bm{A}_n\bm{U}}.  
%\]

\subsection{Examples: acoustic wave equation}

Consider the isotropic acoustic wave equation in pressure-velocity form
\begin{align*}
\pd{p}{t} &= \Div \bm{u}\\
\pd{\bm{u}}{t} &= \Grad p.
\end{align*}
Let $\bm{U}$ denote the group variable $\bm{U} = (p,u,v)$, where $u$ and $v$ are the $x$ and $y$ components of velocity.  Then, in two dimensions, the isotropic wave equation is given as
\[
\pd{\bm{U}}{t} + \pd{\bm{A}_x\bm{U}}{x} + \pd{\bm{A}_y\bm{U}}{y} = 0, \qquad \bm{A}_x = 
\left(\begin{array}{ccc}
0 & 1 & 0\\
1 & 0 & 0\\
0 & 0 & 0
\end{array}
\right), \qquad 
\bm{A}_y = 
\left(\begin{array}{ccc}
0 & 0 & 1\\
0 & 0 & 0\\
1 & 0 & 0
\end{array}
\right).
\]
The normal flux matrix $\bm{A}_n$ is then
\[
\bm{A}_n = 
\left(\begin{array}{ccc}
0 & \bm{n}_x & \bm{n}_y\\
\bm{n}_x & 0 & 0\\
\bm{n}_y & 0 & 0
\end{array}
\right)
\]
implying that the penalty fluxes (with $\bm{W} = \tau\bm{I}$) are 
\[
\avg{\bm{A}_n \bm{U}} - \tau\bm{A}_n^T \jump{\bm{A}_n\bm{U}} = \left(\begin{array}{c}
\avg{\bm{u}_n}\\
\avg{p }\bm{n}_x\\
\avg{p }\bm{n}_y
\end{array}
\right) - 
\tau\left(\begin{array}{c}
\jump{p}\\
\jump{\bm{u_n}}\bm{n}_x\\
\jump{\bm{u_n}}\bm{n}_y
\end{array}
\right)
\]
For $\tau = 1$, these fluxes coincide with the upwind fluxes for isotropic media.  We note that the penalty flux affects only the normal component of the velocity; this is in contrast to Lax-Friedrichs-type fluxes, which penalize component-wise discontinuities in the velocity.

\note{Skew-symmetric discretization for constant coefficient problems \cite{kopriva2014energy}.  For wave propagation, can wrap variable coefficients into $A_0$ \cite{chan2016weight1,chan2016weight2}}.

@@

\note{Define spaces and show that $\bm{S}$ is symmetric definite based on DG discretization.}

We adapt the proof presented in \cite{Warburton20063205} to show that the spectra of $\bm{K}$ splits into two sets as $\tau\rightarrow \infty$, the first of which approaches the eigenvalues of $\bm{A}$, and the second of which moves left of the imaginary axis at a rate of $O(\tau)$.

We begin by splitting the DG approximation space into a conforming part $V^C$ and a non-conforming part $V^{NC}$.  Let $V$ be the DG approximation space
\[
V = \LRc{ u \in L^2(\Oh) : \left.u\right|_{D^k} \in P^N(D^k)}.  
\]
The conforming space $V^{C}$ is then defined as
\begin{equation}
V^{C} = \LRc{ u(\bm{x}) \in V: }
\label{eq:conf}
\end{equation}
We can similarly define the non-conforming approximation space $V^{NC}$ as the orthogonal complement of $V^{C}$, such that the full approximation space $V$ is 
\[
V = V^C \oplus V^{NC}.  
\]

This induces a block decomposition
\[
\bm{K} = \left(\begin{array}{cc}
\bm{A} & \bm{B}\\
-\bm{B}^T & \bm{C} + \tau \bm{S}
\end{array}\right).
\]
We first consider the spectra of $\bm{C} + \tau\bm{S}$.  By the construction of the DG formulation $\bm{C}$ is skew-symmetric, while $\bm{S}$ is symmetric and negative-definite.  Let $\lambda, \bm{u}$ be an eigenpair of $\bm{C} + \tau{\bm{S}}$ corresponding to the largest $N^D$ eigenvalues. Let $\lambda = \alpha + i\beta$ and $\bm{u} = \bm{v} + i\bm{w}$, where $\alpha,\beta$ and $\bm{v},\bm{w}$ are the real and imaginary parts of $\lambda$ and $\bm{u}$, respectively.  Then, expanding and grouping terms in
\[
(\bm{C}+\tau\bm{S})(\bm{v} + i\bm{w}) = (\alpha + i\beta) (\bm{v} + i\bm{w})
\]
we have that
\begin{align*}
(\bm{C}+\tau\bm{S})\bm{v} &= \alpha\bm{v}-\beta\bm{w}\\
(\bm{C}+\tau\bm{S})\bm{w} &= \beta\bm{v}+\alpha\bm{w}.
\end{align*}
Assuming that $\bm{u}^*\bm{u} = \nor{\bm{v}}^2 + \nor{\bm{w}}^2 = 1$, multiplying both sides by $\bm{v}^T,\bm{w}^T$ and straightforward manipulations %yield
%\begin{align*}
%\bm{v}^T\bm{A}\bm{v} &= \alpha\nor{\bm{v}}^2-\beta\bm{v}^T\bm{w}\\
%\bm{w}^T\bm{A}\bm{w} &= \beta\bm{w}^T{\bm{v}}+\alpha\nor{\bm{w}}^2.  
%\end{align*}
%\begin{align*}
%\bm{v}^T\bm{A}\bm{v} + \bm{w}^T\bm{A}\bm{w} &= \alpha\\
%\bm{v}^T\bm{A}\bm{w} - \bm{w}^T\bm{A}\bm{w} &= \beta.
%\end{align*}
using the skew-symmetry of $\bm{C}$ and symmetry of $\bm{S}$ yields
\begin{align*}
\bm{v}^T\bm{C}\bm{w} - \bm{w}^T\bm{C}\bm{w} &= \beta\\
\tau\LRp{\bm{v}^T\bm{S}\bm{v} + \bm{w}^T\bm{S}\bm{w}} &= \alpha.
\end{align*}
Since $\bm{v}^T\bm{C}\bm{w} - \bm{w}^T\bm{C}\bm{w}= 2\bm{w}^T\bm{C}\bm{v} = \beta$ is independent of $\tau$ and $\bm{v},\bm{w}$ are normalized, $\beta$ remains bounded as $\tau\rightarrow \infty$.  Similarly, since $\bm{S}$ is symmetric, negative-definite, and independent of $\tau$, the quantity
\[
\LRb{\bm{v}^T\bm{S}\bm{v} + \bm{w}^T\bm{S}\bm{w}} = \LRb{\frac{\alpha}{\tau}}
\]
is bounded independently of $\tau$, and we conclude that $\LRb{\alpha} = O(\tau)$.  Thus, as $\tau$ increases, the eigenvalues of $\bm{C} + \tau\bm{S}$ are shifted further and further left of the imaginary axis.

We may now show how the spectra of $\bm{K}$ behaves as $\tau \rightarrow \infty$.  Following \cite{Warburton20063205}, let $\bm{U}$ and $\bm{Q}$ be unitary matrices whose columns contain the eigenvectors of $\bm{A}$ and $\bm{C} + \tau \bm{S}$, respectively.  Then, applying a block diagonal similarity transform yields
\[
\left(\begin{array}{cc}
\bm{U}^* & \\
& \bm{Q}^*
\end{array}\right)
\left(\begin{array}{cc}
\bm{A} & \bm{B}\\
-\bm{B}^T & \bm{C} + \tau \bm{S}
\end{array}\right)
\left(\begin{array}{cc}
\bm{U} & \\
& \bm{Q}
\end{array}\right)
 = \left(\begin{array}{cc}
\bm{\Lambda}_C & \bm{U}^T\bm{B}\bm{Q}\\
-\bm{Q}^T\bm{B}^T\bm{U} & \bm{\Lambda}_D
\end{array}\right),
\]
where $\bm{\Lambda}_C,\bm{\Lambda}_D$ are diagonal matrices whose entries consist of eigenvalues of $\bm{A},\bm{C} + \tau\bm{S}$, respectively.  Since $\bm{B}$ is independent of $\tau$, $\nor{\bm{U}^T\bm{B}\bm{Q}}$ can be bounded independently of $\tau$, assuming that $\bm{U}$ and $\bm{Q}$ are normalized.  Gerschgorin's theorem applied to $\bm{\Lambda}_C,\bm{\Lambda}_D$ then implies that the eigenvalues of $\bm{K}$ are contained in two sets of discs with radii independent of $\tau$.  The first set of discs are centered around $\lambda^C_i$ for $i = 1,\ldots,N^C$, while the second set of discs are centered around $\lambda^D_i$ for $i = 1,\ldots,N^D$, where ${\rm Re}(\lambda^D_i) = O(\tau)$.
